Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2023-02-23 paper/paper.tex
Revise section 8

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.
%
This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.
%
We therefore add a response monitor (Resp\_Monitor) to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.
%
And we add a geo-fence monitor (Geofence\_Monitor) to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.
%
The Geofence\_Monitor is a gated monitor in that it prevents the observed automation response from reaching the Waypoint Manager if the zones are violated.
%
Its code contract is shown in \figref{fig:geofence-monitor}.

@@

Writing code contracts for the more complex monitors revealed that although the language is very effective at declarative specifications that define what is being calculated, it is non-intuitive, and sometimes cumbersome, for defining how the computation needs to take place.
%
The primary reason for its unease in describing how computation is performed is that it lacks any type of iterative looping structure for arrays.
%
Instead, it relies on folding and mapping to describe iterative computation which is non-intuitive for many types of array updates.
%
Growing the expressiveness of the language arround arrays is something to investigate in future work.

@@

A fully verified compiler has been developed that takes Lustre and compiles it into assembly code, specified and verified in Coq \cite{10.1145/3140587.3062358}.
%
The key is in combining infinite sequences of data-flow models with incremental manipulation of memories akin to an imperative model.
%
CompCert is used on the backend to create the final rendered executable \cite{compcert}.
%
This work is quite similar to ours in providing a verified compilation chain from Lustre.
%
However, there are significant differences: notably, they tackle a more comprehensive subset of Lustre than our work.
%
We have been able to work effectively with a relatively simple core language, \eg, without \emph{clocking} features.
%
This subset aligns with our contract language, and allows us to generate behaviorally equivalent code so we can show that the generated code meets its logical specification.
%
This, in turn, can be used as a leaf-level claim in a system-wide correctness argument conducted by compositional reasoning in \agr.
%
It is important to note that we target a wholistic systems approach to cyber-security that is integrated into the \agr\ reasoning environment whereas the other work targets more specifically a compiler for Lustre.

@@

As seen in this paper, contracts can be stateful and even higher-order \cite{10.1145/583852.581484}.
%
Verification aware languages compile contracts to runtime monitors \cite{10.1007/978-3-642-28869-2_11}, or omit them when they can statically prove that the code preserves the contract under all possible inputs and executions \cite{10.1145/3158139}.
%
Dafny is a notable verification aware language that provides a contract language, an implementation language, a proof engine to show if an implementation adheres to the contract, and backend compilers for several different target platforms \cite{dafny}.
%
Dafny contracts provide the verification conditions to prove out the implementation code and are not compiled.
%
Compared to the work discussed in this paper, our test contracts are more similar to the Dafny contracts as they are also not compiled and only serve to prove properties of the code contracts.
%
In that regard, the code contracts are the implementation, but unlike Dafny, \ckml\ provide a verified compilation path to binaries.

>>>>

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.
%
This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.
%
We therefore add a response monitor (Resp Monitor) to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.
%
And we add a geo-fence monitor (Geofence Monitor) to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.
%
The Geofence\_Monitor is a gated monitor in that it prevents the observed automation response from reaching the Waypoint Manager if the zones are violated.
%
Its code contract is shown in \figref{fig:geofence-monitor}.

@@

Writing code contracts for the more complex monitors revealed that although the language is very effective at declarative specifications that define what is being calculated, it is non-intuitive, and sometimes cumbersome, for defining how the computation needs to take place.
%
The primary reason for its unease in describing how computation is performed is that it lacks any type of iterative looping structure for arrays.
%
Instead, it relies on folding and mapping to describe iterative computation which is non-intuitive for many types of array updates.
%
Growing the expressiveness of the language around arrays is something to investigate in future work.

@@

A fully verified compiler has been developed that takes Lustre and compiles it into assembly code, specified and verified in Coq \cite{10.1145/3140587.3062358}.
%
The key is in combining infinite sequences of data-flow models with incremental manipulation of memories akin to an imperative model.
%
CompCert is used on the backend to create the final rendered executable \cite{compcert}.
%
This work is quite similar to ours in providing a verified compilation chain from Lustre.
%
However, there are significant differences: notably, they tackle a more comprehensive subset of Lustre than our work.
%
We have been able to work effectively with a relatively simple core language, \eg, without clocking features.
%
This subset aligns with our contract language, and allows us to generate behaviorally equivalent code so we can show that the generated code meets its logical specification.
%
This, in turn, can be used as a leaf-level claim in a system-wide correctness argument conducted by compositional reasoning in \agr.
%
It is important to note that we target a wholistic systems approach to cyber-security that is integrated into the \agr\ reasoning environment whereas the other work targets more specifically a compiler for Lustre.

@@

As seen in this paper, contracts can be stateful and even higher-order \cite{10.1145/583852.581484}.
%
Verification aware languages compile contracts to runtime monitors \cite{10.1007/978-3-642-28869-2_11}, or omit them when they can statically prove that the code preserves the contract under all possible inputs and executions \cite{10.1145/3158139}.
%
Dafny is a notable verification aware language that provides a contract language, an implementation language, a proof engine to show if an implementation adheres to the contract, and backend compilers for several different target platforms \cite{dafny}.
%
Dafny contracts provide the verification conditions to prove out the implementation code and are not compiled.
%
Compared to the work discussed in this paper, our test contracts are more similar to the Dafny contracts as they are also not compiled and only serve to prove properties of the code contracts.
%
In that regard, the code contracts are the implementation, but unlike Dafny, \ckml\ provides a verified compilation path to binaries.
